Community-conditioned language models for linguistic variation

### 2021-12-12 paper/paper1.tex
small edits

Using \texttt{langid.py} \citep{Lui2012}, we observe that a majority of the overall
messages are classified as English (94.6\% of the test set) and X of \num{510} communities %TODO
have more than half of their messages classified as English.\footnote{See \cref{sec:ethics} for futher
  discussion.}

@@

The paper does not include any text that could be linked back to 
personally identifiable information.
We do release our trained community embeddings, but the dimensionality 
is low enough that we believe it would be impossible to reproduce 
personally identifiable information from them.

\paragraph{Language identification}
As discussed in section \cref{sec:data}, we decided not to filter our data for non-English 
comments.
Although our focus in this paper is intra-language variation, 
language identification has the potential to introduce bias by reinforcing hegemonic
language classes and the boundaries between them.
In our case, filtering out messages classified as non-English would bias the 
dataset away from non-standard and code-switched language varieties,
which are of interest in the current work.

>>>>

Using \texttt{langid.py} \citep{Lui2012}, we observe that a majority of the overall
messages are classified as English (94.6\% of the test set) and X of \num{510} communities %TODO
have more than half of their messages classified as English.
Given the small amount of non-English data, 
we decided that the bias introduced by attempting to filter message
by language outweighted the potential benefits of doing so.\footnote{
  See \cref{sec:ethics} for futher discussion.}

@@

The paper does not include any text that could be linked back to 
personally identifiable information.
We do release our trained community embeddings, but they have 
low dimensionality and pose a low risk for exposing personally
identifiable information.

\paragraph{Language identification}
As mentioned in section \cref{sec:data}, we decided not to filter our data for non-English 
comments.
Although our focus in this paper is intra-language variation, 
language identification has the potential to introduce bias by reinforcing hegemonic
language classes and the boundaries between them.
In our case, filtering out messages classified as non-English would bias the 
dataset away from non-standard and code-switched language varieties,
which are of interest in the current work.
